---
output:
  html_document: default
  word_document: default
---
set.seed(123)

sim<- rexp(10000,rate = 0.0001)

hist(sim,main = 'Simulated random values of exp', col = 'red' )
```{r}
for(i in 1:10){
  print(seq(1,5))
}
```
```{r}
x<- rexp(500,0.001)
hist(x)

```



mean_sim<- mean(sim)

var_sim<- var(sim)

#Theoritical values of mean and Variance

T_mean<- 1/0.0001

T_var<- 1/0.0001^2

T_mean
T_var

M<- 20000

y<- pmin(sim,M)
z<- pmax(0,sim-M)

mean_y<- mean(y)

mean_z <- mean(z)


z.mean <- function(M) {
  z <- pmax(0,sim-M)
  z.mean<- mean(z)
}

z.var<- function(M){
  z<- pmax(0,sim-M)
  z.var<- var(z)
}

z_5000_var<-z.var(5000)
mean_sim
var_sim

T_mean

T_var

z_5000


y.mean<- function(M){
  y<- pmin(sim,M)
  y.mean<- mean(y)
}
y.var<- function(M){
  y<- pmin(sim,M)
  y.var<- var(y)
}

M_vector<- c(5000,10000,30000,40000,50000)

y_mean<- y.mean(M_vector) 
y_var<- y.var(M_vector)

z_mean<- z.mean(M_vector)
z_var<- z.var(M_vector)

y_mean
y_var
z_mean
z_var
